\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-29 metatheory-condensed.tex
make Wrec arity 3

W-types are eliminated with the form $\Wrec{\lkg}{t}$, where $t$ is of a
W-type $\El{\wcode{\wsig}}$, and $\lkg$ is essentially an $n$-tuple of
case handlers for the $n$ constructors in~$\wsig$ (\ruleref{tm/wrec}).
Each case handler has a type of the form $\CaseSig{A}{B}{T}$, where
$T$ is the motive of the recursion (\ruleref{ty/casety}).
This collection of case handlers then encodes those defined or inherited
by an \lsti{FRecursion} command in our plugin.
We choose to type it with a linkage type $\TyLkg{\RecSig{\wsig}{T}}$
to avoid introducing $n$-tuples, which linkages generalize.

Rules \ruleref{tm/wsup} and \ruleref{tm/wrec} require knowing~$\wsig$:
the W-type is exhaustively generated by its constructors, and
its elimination must exhaustively handle all the constructors in
its signature.
%Notice that rule \ruleref{tm/wrec} requires knowing~$\wsig$:
%typing a recursive function $\lam{\Wrec{\lkg}{\var{0}}}$ must check
%that the case handlers~$\lkg$ exhaustively handle all the constructors
%in the W-type signature~$\wsig$.

In contrast, $\wsig$ should be hidden from the typing context of any
term that does not invoke $\texttt{Wsup}$ or $\texttt{Wrec}$, so that
the term can be reused---without being rechecked---for a different
W-type signature~$\wsig'$ that extends~$\wsig$ with additional
constructors.
Moreover, the typing of the term should be made polymorphic to
the definitions of those fields that invoke $\texttt{Wsup}$ or $\texttt{Wrec}$,
so that the term can be reused---without being rechecked---when those fields
are overridden to support the extended signature~$\wsig'$.

@@

{\goodTerm{\Gm}{\wsup{T}{a}{b}}{\El{(\wcode{\wsig})}} }

@@

{\goodTerm{\Gm}{\Wrec{w}{r}}{R}}

@@

{\goodTerm{\Gamma}{\Wrec{h}{(\wsup{\wsig}{a}{b})} \equiv 
(\app{((\app{(\Recproj{j}{h})} )[("id", a)])} )[("id", \lam{(\Wrec{h[\pi_1]}{b})})]

>>>>

W-types are eliminated with the form $\Wrec{\wsig}{\lkg}{t}$, where $t$ is of a
W-type $\El{\wcode{\wsig}}$, and $\lkg$ is essentially an $n$-tuple of
case handlers for the $n$ constructors in~$\wsig$ (\ruleref{tm/wrec}).
Each case handler has a type of the form $\CaseSig{A}{B}{T}$, where
$T$ is the motive of the recursion (\ruleref{ty/casety}).
This collection of case handlers then encodes those defined or inherited
by an \lsti{FRecursion} command in our plugin.
We choose to type it with a linkage type $\TyLkg{\RecSig{\wsig}{T}}$
to avoid introducing $n$-tuples, which linkages generalize.

Rules \ruleref{tm/wsup} and \ruleref{tm/wrec} require knowing~$\wsig$:
the W-type is exhaustively generated by its constructors, and
its elimination must exhaustively handle all the constructors in
its signature.

In contrast, $\wsig$ should be hidden from the typing context of any
term that does not invoke $\Wsup{\wsig}{\cdot}{\cdot}$ or $\Wrec{\wsig}{\cdot}{\cdot}$, so that
the term can be reused---without being rechecked---for a different
W-type signature~$\wsig'$ that extends~$\wsig$ with additional
constructors.
Moreover, the typing of the term should be made polymorphic to
the definitions of those fields that invoke $\texttt{Wsup}$ or $\texttt{Wrec}$,
so that the term can be reused---without being rechecked---when those fields
are overridden to support the extended signature~$\wsig'$.

@@

{\goodTerm{\Gm}{\Wsup{T}{a}{b}}{\El{(\wcode{\wsig})}} }

@@

{\goodTerm{\Gm}{\Wrec{\wsig}{w}{r}}{R}}

@@

{\goodTerm{\Gamma}{\Wrec{\wsig}{h}{(\Wsup{\wsig}{a}{b})} \equiv 
(\app{((\app{(\Recproj{j}{h})} )[("id", a)])} )[("id", \lam{(\Wrec{\wsig}{h[\pi_1]}{b})})]
